### 2020-08-08 thesis/thesis.tex
[thesis] Uncomment chapters 4-7

TODO Describe what is data-flow analysis \\

TODO Give example for constant folding \\

TODO Propose analysis on imaginary CFG Not sure if it makes sense?

@@

@@

    \begin{verbatim}
    handle ... with {
        Choice p r ->
            let t <- r 1 in
            let f <- r 0 in
            <PLACEHOLDER> |
        return x -> return x
    }
    \end{verbatim}
    where in the \verb!<PLACEHOLDER>! we can define on what to do with the
    computation. For example, min-max strategy for picking the minimum value:

@@

    TODO subset of this section's content is explained already

@@

    % Outdated
    As of this day, two implementations are available, one based on the curried
    translation and Appel~\cite{appel-continuations}, and the second one based
    directly on the uncurried translation with continuations as explicit stacks
    from paper. More details can be found in Section~\ref{chapter:implementation}.
    All commands are available within \verb!src!  directory.

@@

    TODO Extend language with basic constructs for usability

@@

    TODO Rewrite here operational semantics from Links paper

@@

    The Freak implementation is available at \href{https://github.com/Tomatosoup97/freak}{\underline{https://github.com/Tomatosoup97/freak}},
    written purely in Haskell. While the paper provided a good overview of the
    language and the translation, the lower-level details were omitted. That
    being said, two inherently different takes at the implementations were made.
    The first one is based on curried translation and A. Appel~\cite{appel-continuations}
    book, and the second one directly on the uncurried translation to target
    calculus with continuations represented as explicit stacks from the paper.
    We start by presenting core data structures, and afterwards move to actual
    translation details.

@@

    TODO Drop of continuations is still an issue

@@

    TODO Simple implementation for cohandlers

>>>>

\noindent
- TODO Describe what is data-flow analysis \\
- TODO Give example for constant folding \\
- TODO Propose analysis for coalgebraic effects. Not sure if that's not too much,
as it's not the goal of this thesis. Definitealy leave this section for later.

@@

\noindent
TODO muuuch longer explanation of this topic

@@

    \begin{verbatim}
    handle ... with {
        Choice p r ->
            let t <- r 1 in
            let f <- r 0 in
            <PLACEHOLDER> |
        return x -> return x
    }
    \end{verbatim}
    where in the \verb!<PLACEHOLDER>! we can define what to do with the
    computation. For example, min-max strategy for picking the minimum value:

@@

    \noindent
    TODO subset of this section's content is explained already

@@

    % Outdated
    As of this day, two implementations are available, one based on the curried
    translation and Appel~\cite{appel-continuations}, and the second one based
    directly on the uncurried translation with continuations as explicit stacks
    from paper. More details can be found in Section~\ref{chapter:implementation}.
    All commands are available within the \verb!src! directory.

@@

    \noindent
    TODO Extend language with basic constructs for usability

@@

    \noindent
    TODO Rewrite here operational semantics from Links paper

@@

    The Freak implementation is available on github~\cite{freak}, written purely
    in Haskell. While the paper provided a good overview of the language and the
    translation, the lower-level details were omitted. That being said, two
    inherently different takes at implementations were made. The first one
    is based on curried translation and A. Appel~\cite{appel-continuations}
    book, and the second one directly on the uncurried translation to target
    calculus with continuations represented as explicit stacks from the paper.
    We start by presenting core data structures, and afterwards move to actual
    translation details.

@@

    \noindent
    TODO Drop of continuations is still an issue

@@

    \noindent
    TODO Simple implementation for cohandlers
